### 2019-05-24 doc/chapters/towards_verifying.tex
added stainless output
rewriting & BigInt

\subsection{Rewriting Usage of BigInt \&-Function}

>>>>

\subsection{Rewriting Usage of BigInt \&-Function}
Stainless output:
\begin{lstlisting}
  [ Error  ] NumberType.scala:19:14: Unknown call to & on result (BigInt) with
             arguments List(Number.this.andMask) of type List(BigInt)
             require((result & andMask) == result,
\end{lstlisting}
Due to the restrictions on BigInt, the \& function on it is not supported too.
\begin{lstlisting}
  sealed abstract class Number extends BasicArithmetic[Int64] {
    def andMask: BigInt

    override def +(num: Int64): Int64 = apply(checkResult(underlying + num.underlying))

    private def checkResult(result: BigInt): BigInt = {
      require((result & andMask) == result, "Result was out of bounds, got: " + result)
      result
    }
  }
\end{lstlisting}
This is a bound check.
It checks, if the result of the addition is in range of the specified type (Int64 here).
So here the \& mask can be replaced with a bound check whether the result is in range of Long.MinValue and Long.MaxValue.
Again the code gets a bit more static but for this usecase its ok.
